---
title: ""
author: ""
date: ""
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    smooth_scroll: false
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(reshape2)
library(tidyverse)
library(rtracklayer)
library(isoband)
library(sf)
library(MASS)
library(lwgeom)
library(ggrepel)
library(hexbin)
library(ggrastr)
library(viridis)
library(pals)
library(patchwork)
library(highcharter)
library(dplyr)
library(GenomicRanges)
library(reactable)
```

```{r echo = FALSE, warning=FALSE,message=FALSE,out.width='100%'}
setwd("~/Documents/hnscc_chipseq/nsd2oe")
wd <- paste0("~/Documents/hnscc_chipseq/nsd2oe")
```

# NSD1KO-NSD2OE v PA

## Clusters
```{r echo = FALSE, warning=FALSE,message=FALSE,fig.width=8,fig.height=3}
load("~/Documents/hnscc_chipseq/nsd2oe/plots/Cal27.PA.NSD2OE.K36me2.clus.fig.rda")
ps$Cal27
cell_line=paste0("Cal27")
control=paste0("PA")
test=paste0("NSD2OE")
mark=paste0("K36me2")
```

## Annotations - cluster A {.tabset}

### Ensembl regulatory build {.tabset .tabset-pills}

#### Genome-wide

Genome-wide enrichment of open chromatin in cluster A, but not necessarily in IGR. 
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(sprintf("%s/plots/Cal27.PA.NSD2OE.K36me2.ensembl.ol.plot.enrich.rda",wd))
p1 <- ensembl.ol.plot.enrich
load("~/Documents/hnscc_chipseq/nsd2oe/plots/Cal27.PA.NSD2OE.K36me2.ensembl.ol.plot.dep.rda")
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR

No significant enrichment in IGR, but there is significant depletion in promoter flanking region, promoter, CTCF binding site and enhancer.

```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(sprintf("%s/plots/Cal27.PA.NSD2OE.K36me2.ensembl.ol.plot.enrich.igr.rda",wd))
p1 <- ensembl.ol.plot.enrich
load("~/Documents/hnscc_chipseq/nsd2oe/plots/Cal27.PA.NSD2OE.K36me2.ensembl.ol.plot.dep.igr.rda")
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(sprintf("%s/plots/Cal27.PA.NSD2OE.K36me2.ensembl.ol.plot.enrich.g.rda",wd))
p1 <- ensembl.ol.plot.enrich
load("~/Documents/hnscc_chipseq/nsd2oe/plots/Cal27.PA.NSD2OE.K36me2.ensembl.ol.plot.dep.g.rda")
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)

```

### ENCODE cCRE {.tabset .tabset-pills}

#### Genome-wide
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR

In cluster A, which has indiscriminate increases in K36me2, we may see enrichment in CTCF binding sites, but not necessarily restored enhancer function. NSD1-mediated K36me2-marked enhancer function may still not be completely recovered.

```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic

```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

### RepeatMasker {.tabset .tabset-pills}

#### Genome-wide

Genome-wide enrichment of LTR, LINE and satellite repeats.

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic 
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

---

# NSD2KO v PA

## Clusters
```{r echo = FALSE, warning=FALSE,message=FALSE,fig.width=8,fig.height=3}
load("~/Documents/hnscc_chipseq/nsd2oe/plots/Cal27.PA.NSD2KO_c1.K36me2.clus.fig.rda")
ps$Cal27
cell_line=paste0("Cal27")
control=paste0("PA")
test=paste0("NSD2KO_c1")
mark=paste0("K36me2")
```

## Annotations - cluster A {.tabset}

### Ensembl regulatory build {.tabset .tabset-pills}

#### Genome-wide
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ensembl.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- ensembl.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ensembl.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ensembl.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- ensembl.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ensembl.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ensembl.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- ensembl.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ensembl.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

### ENCODE cCRE {.tabset .tabset-pills}

#### Genome-wide
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR

```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic

```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

### RepeatMasker {.tabset .tabset-pills}

#### Genome-wide

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic 
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

---

# NSD1KO v NSD2KO

## Clusters
```{r echo = FALSE, warning=FALSE,message=FALSE,fig.width=8,fig.height=3}
load("~/Documents/hnscc_chipseq/nsd2oe/plots/Cal27.NSD1KO.NSD2KO_c1.K36me2.clus.fig.rda")
ps$Cal27
cell_line=paste0("Cal27")
control=paste0("NSD1KO")
test=paste0("NSD2KO_c1")
mark=paste0("K36me2")
```

## Annotations - cluster A {.tabset}

### Ensembl regulatory build {.tabset .tabset-pills}

#### Genome-wide
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ensembl.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- ensembl.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ensembl.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ensembl.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- ensembl.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ensembl.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ensembl.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- ensembl.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ensembl.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

### ENCODE cCRE {.tabset .tabset-pills}

#### Genome-wide
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR

```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic

```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

### RepeatMasker {.tabset .tabset-pills}

#### Genome-wide

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic 
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```


---

# NSD1KO v NSD.DKO

## Clusters
```{r echo = FALSE, warning=FALSE,message=FALSE,fig.width=8,fig.height=3}
load("~/Documents/hnscc_chipseq/nsd2oe/plots/Cal27.NSD1KO.DKO_2.K36me2.clus.fig.rda")
ps$Cal27
```